Resilience and Home-Space for WSTS \thanks{This work was partly done while the authors were supported by the Agence Nationale de la Recherche grant BraVAS (ANR-17-CE40-0028).}

### 2023-10-26 VMCAI-revised-version/final.tex
up

In the case of $\pred$-basis-effective upward compatible WSTS, {\sc Resilience} is undecidable when $\Safe = \mathop{\downarrow} \Safe$.  This stems from the fact
{\sc Resilience} when $\Safe= \{ q_f({\bf 0}) \}$ for some control-state $q_f$ is equivalent to
deciding structural termination of reset-VASS, which is undecidable.

Indeed, the structural termination problem consists in deciding if %the termination problem holds for 
a system terminates on every initial state.

\problemx{Structural termination}
{A reset-VASS $V=(Q,T)$ of dimension $d$.}
{ %$Q \times \N^d \longrightarrow^{*} q_f({\bf 0})$ ? 
Do all runs for every initial state terminate ?\\}

@@

\begin{proof}
\nocite{araki1976PN,dufourd1998reset}
{\sc Resilience} when $\Safe= \{ q_f({\bf 0}) \}$ for some state $q_f$ is equivalent to
deciding structural termination of reset-VASS,
since termination is w.l.o.g. reachability of $q_f({\bf 0})$ 
 \mathieu{est-ce qu'on a pas besoin d'une hypothèse d'être deterministic ici pour que ce soit vraiment w.l.o.g. ??} 
\alain{qu'entends-tu par deterministic ici ?}
for some control state $q_f$. \qed \end{proof}

>>>>

In the case of $\pred$-basis-effective upward compatible WSTS, {\sc Resilience} is undecidable when $\Safe = \mathop{\downarrow} \Safe$.  This stems from the fact
{\sc Resilience} when $\Safe= \{ q_f({\bf 0}) \}$ for some control-state $q_f$ is equivalent to
deciding structural %termination of reset-VASS, 
			existential halting of reset-VASS, 
which is undecidable.

Indeed, the structural existential halting problem consists in deciding if 
a system %terminates
have a terminating (i.e. finite) run
 from every initial state.

% \problemx{Structural universal halting}
% {A reset-VASS $V=(Q,T)$ of dimension $d$.}
% { Do all runs for every initial state terminate ?\\}

\problemx{Structural existential halting}
{A reset-VASS $V=(Q,T)$ of dimension $d$.}
{ For every initial state, does there exists a run that terminates ?\\}

@@

\begin{proof}
\nocite{araki1976PN,dufourd1998reset}
{\sc Resilience} when $\Safe= \{ q_f({\bf 0}) \}$ for some state $q_f$ is equivalent to {\sc Structural existential halting} of reset-VASS,
since a run terminates w.l.o.g. if it reaches a terminal state of the form $q_f({\bf 0})$. \qed \end{proof}
